Data_visualization

### 2018-09-24 Rmd/Data_visualization_common_names.Rmd
density plot
adding some text for R

###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

@@

\newpage
###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)
```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

###STIGMA AREA

@@

>>>>

###SEED SET PER SPECIES WITH DIFFERENT TREATMENTS

Light blue:Brassicaceae, orange: Convolvulaceae, green:Solanaceae, grey: xenogamy, autogamy and controls
```{r,message=FALSE, warning=FALSE, echo=FALSE, cache=FALSE, fig.height=6, fig.width=7,out.width='100%'}
#Preparing seed set plots, starting with Petunia

@@

\newpage
###POLLEN MIX RATIOS PER FAMILY -3 NEXT PAGES- (N=3)

Each histogram shows the pollen ratio in percentage of the focal and non-focal species. The barplots are organized per family.

```{r, message=FALSE, warning=FALSE, echo=FALSE,fig.width=8}
pollen_ratios_brassicaceae <- read.csv("Data/pollen_ratios_brassicaceae.csv", header = T)
ggplot(pollen_ratios_brassicaceae, aes(x=spp, y=ratio, fill=variable)) +
  geom_bar(stat='identity', position='dodge') +labs(title="Brassicaceae", x="", y="Pollen mix ratio") + 
  theme(axis.text.x=element_text(angle=60,hjust=1))+geom_hline(yintercept = 50)+
  scale_fill_manual(values=c("grey10", "grey60"))+ ylim(0,100)

@@

###STIGMA AREA. BRASSICACEAE+1 AND SOLANACEAE+1

@@

###STIGMA AREA. ALL SPECIES, COLOUR PER SPECIES AND FAMILY

I like this type of density plot and I wanted to show the differences of stigma area of our 3 familys. The x axis shows the area in micrometers (um^2).
